Clustering in a hyperbolic model of complex networks.

### 2019-02-21 concentration.tex
typos in section 9.3

We start with analyzing joint neighborhoods in $\Gbox$. Let $p, p^\prime \in \Rcal$. Then we denote by $\Ncal_{\text{box}}(p\Delta p^\prime)$ the number of disjoint neighbors of $p$ and $p^\prime$ in $\Gbox$, i.e. those points that belong to either $\BallPon{p}$ or $\BallPon{p^\prime}$ but not to their intersection. In addition we denote by $\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$. We shall establish lower bounds on the expect number of these disjoint neighbors $\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number of joint neighbors. For this we will distinguish between the cases where the distance between the $x$-coordinates of $p$ and $p^\prime$ is small or large. Figure~\ref{fig:representation_disjoint_neighborhoods_P_n}-\ref{fig:representation_disjoint_neighborhoods_P_n_3} show the different situations that occur.

@@

We start by analyzing the shape of the neighborhoods. Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$ and $y^\prime \le y$. To understand the computation it is helpful to have a picture of the different situations. Figure \ref{fig:representation_disjoint_neighborhoods_P_n} and Figure \ref{fig:representation_disjoint_neighborhoods_P_n_2} show two different situations for small distance in the $x$-coordinates, in which case the number of disjoint neighbors is small. The case where this distance is large, and the number of disjoint neighbors is expected to be large, is show in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}. There are several different quantities that are important. The first are the heights $h_1(p^\prime)$ and $h_2(p^\prime)$ where, respectively, the left and right boundaries of the ball $\BallPon{p^\prime}$ go outside the box $\Rcal$. Note that when $x = 0$ then these height are the same and we denote this by $h(y)$. We also need to know the coordinates $h(p,p^\prime)$ and $x^\ast(p,p^\prime)$ of the intersection of the right boundary of the neighborhood of $p$ with the left boundary of the neighborhood of $p^\prime$. Finally we will denote by $d(p,p^\prime)$ the distance between the lower right boundary of $\BallPon{p}$ and the lower left of $\BallPon{p^\prime}$, which is positive only when the bottom parts of both neighborhoods do not intersect, compare Figures \ref{fig:representation_disjoint_neighborhoods_P_n} and \ref{fig:representation_disjoint_neighborhoods_P_n_3}. The full expressions of all these functions are given below for further reference.

\begin{align}
	h(y) &= R_n - y + 2\log\left(\frac{\pi}{2}\right) \label{eq:def_height_y_P_n}\\
	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R_n}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R_n}{2}} - x^\prime\right) - y^\prime 
		\label{eq:def_height_right_P_n} \\
%	\iota_x(p,p^\prime) &= \frac{(x^\prime-x)e^{\frac{y}{2}}}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}
%		\label{eq:def_x_intersection_close_boundaries}\\
%	\iota_y(p,p^\prime) &= 2\log\left(\frac{x^\prime - x}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}\right)
%		\label{eq:def_y_intersection_close_boundaries}\\
	h((p,p^\prime) &= 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
	x^\ast(p,p^\prime) &= \frac{x e^{\frac{y^\prime}{2}} + x^\prime e^{\frac{y}{2}}}{e^{\frac{y}{2}} + 	
		e^{\frac{y^\prime}{2}}},\\
	d(p,p^\prime) &= |x - x^\prime| - \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right).
	\label{eq:def_d_p_p_prime}
\end{align}

>>>>

We start with analyzing joint neighborhoods in $\Gbox$. Let $p, p^\prime \in \Rcal$. Then we denote by $\Ncal_{\text{box}}(p\Delta p^\prime)$ the number of disjoint neighbors of $p$ and $p^\prime$ in $\Gbox$, i.e. those points that belong to either $\BallPon{p}$ or $\BallPon{p^\prime}$ but not to their intersection. In addition we denote by $\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$. We shall establish lower bounds on the expected number of these disjoint neighbors $\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number of joint neighbors. For this we will distinguish between the cases where the distance between the $x$-coordinates of $p$ and $p^\prime$ is small or large. Figure~\ref{fig:representation_disjoint_neighborhoods_P_n}-\ref{fig:representation_disjoint_neighborhoods_P_n_3} show the different situations that occur.

@@

We start by analyzing the shape of the neighborhoods. Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$ and $y^\prime \le y$. To understand the computation it is helpful to have a picture of the different situations. Figure \ref{fig:representation_disjoint_neighborhoods_P_n} and Figure \ref{fig:representation_disjoint_neighborhoods_P_n_2} show two different situations for small distance in the $x$-coordinates, in which case the number of disjoint neighbors is small. The case where this distance is large, and the number of disjoint neighbors is expected to be large, is shown in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}. There are several different quantities that are important. The first are the heights $h_1(p^\prime)$ and $h_2(p^\prime)$ where, respectively, the left and right boundaries of the ball $\BallPon{p^\prime}$ go outside the box $\Rcal$. Note that when $x = 0$ then these heights are the same and we denote this by $h(y)$. We also need to know the coordinates $h(p,p^\prime)$ and $x^\ast(p,p^\prime)$ of the intersection of the right boundary of the neighborhood of $p$ with the left boundary of the neighborhood of $p^\prime$. Finally we will denote by $d(p,p^\prime)$ the distance between the lower right boundary of $\BallPon{p}$ and the lower left of $\BallPon{p^\prime}$, which is positive only when the bottom parts of both neighborhoods do not intersect, compare Figures \ref{fig:representation_disjoint_neighborhoods_P_n} and \ref{fig:representation_disjoint_neighborhoods_P_n_3}. The full expressions of all these functions are given below for further reference.

\begin{align}
	h(y) &= R_n - y + 2\log\left(\frac{\pi}{2}\right) \label{eq:def_height_y_P_n}\\
	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R_n}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R_n}{2}} - x^\prime\right) - y^\prime 
		\label{eq:def_height_right_P_n} \\
%	\iota_x(p,p^\prime) &= \frac{(x^\prime-x)e^{\frac{y}{2}}}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}
%		\label{eq:def_x_intersection_close_boundaries}\\
%	\iota_y(p,p^\prime) &= 2\log\left(\frac{x^\prime - x}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}\right)
%		\label{eq:def_y_intersection_close_boundaries}\\
	h(p,p^\prime) &= 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
	x^\ast(p,p^\prime) &= \frac{x e^{\frac{y^\prime}{2}} + x^\prime e^{\frac{y}{2}}}{e^{\frac{y}{2}} + 	
		e^{\frac{y^\prime}{2}}},\\
	d(p,p^\prime) &= |x - x^\prime| - \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right).
	\label{eq:def_d_p_p_prime}
\end{align}
